---
title: "Data overlaying on Rayshader rendering"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: inline
---

In this notebook, we are going to overlay Seoul's subway routes on Rayshader rendering.

## Import

```{r message=FALSE, warning=FALSE}
library(rayshader)
library(raster)
library(magrittr)
library(esri2sf)
```


## Get DEM data 

Get NASA's SRTM 30m grid elevation data. Convenient tool for this:
http://dwtkns.com/srtm30m/


We need two rasters, N37E126 and N37E127. We are going to merge these two rasters
and crop it so that the raster contains downtown Seoul. 

```{r}
tif1 <- raster("../data/N37E126.hgt")
tif2 <- raster("../data/N37E127.hgt")
merged <- merge(tif1, tif2,tolerance=0.01)

cx <- 126.9761
cy <- 37.5775
r <- 0.079
ext <- extent(cx-r, cx+r, cy-r, cy+r)
city <- crop(merged, ext) 
```


Convert the raster to elevation matrix

```{r}
elmat <- matrix(extract(city, extent(city)),
               nrow=nrow(city),
               ncol=ncol(city))
```


## Get subway routes.

Pull subway routes from ArcGIS server at National Geographic Information Institute of Korea(ngii.go.kr) 
and convert them into sf format using esri2sf package.

```{r message=FALSE, warning=FALSE}
rail <- "http://sd.ngii.go.kr:6080/arcgis/rest/services/NGII_EMAP/MapServer/502" %>%
  esri2sf()
```

Rasterize sf and convert the raster to matrix.

```{r message=FALSE, warning=FALSE}
rail_raster <- raster(ncol=ncol(city), nrow=nrow(city))
rail_raster <- setExtent(rail_raster, extent(city))
rail_raster <- rasterize(rail, rail_raster, 1, background=0)
rail_mat <- matrix(extract(rail_raster, extent(rail_raster)),
               nrow=nrow(rail_raster),
               ncol=ncol(rail_raster))
rail_mat <- rail_mat[, ncol(rail_mat):1]  # flip
```


### 2d plot

Render the elevation matrix and give ambient and ray shades.

```{r message=FALSE, warning=FALSE}
z <- 100
model <- elmat %>%
  sphere_shade(texture = "imhof2", sunangle = 200) %>%
  add_shadow(ambient_shade(elmat, zscale=z, anglebreaks = seq(65, 65, 1))) %>%
  add_shadow(ray_shade(elmat, zscale=z, lambert=FALSE, anglebreaks = seq(65, 65, 1))) %>%
  add_water(rail_mat, color=col2rgb('#000000')) # for subway routes
  
```

Plot 2D

```{r}
model %>% plot_map()
```

Plot 3D

```{r message=FALSE, warning=FALSE}
model %>%  
  plot_3d(elmat, zscale=8, 
          soliddepth=-60, 
          windowsize = c(1200, 1200), 
          fov=60, 
          water=TRUE)
```


